---
title: "Test Report Pkg"
author: "John Minter"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

# Introduction

`Report` - from R to manuscript

report’s primary goal is to bridge the gap between R’s output and the
formatted results contained in your manuscript. It automatically produces
reports of models and dataframes according to best practice guidelines
(e.g., APA’s style guide), ensuring standardization and quality in results
reporting.

# To install

```
install.packages("devtools")
install.packages("parameters")
devtools::install_github("easystats/report")
library(devtools)
install_github("easystats/parameters")
library("report")
```

# Test

```{r loadPackages}
library(report)
library(parameters)
library(dplyr)
library(kableExtra)
```

## Example 1

```{r exampleOne, comment=NA}
model <- lm(Sepal.Length ~ Species, data=iris)
report(model)
```

## Example 2

These reports nicely work within the tidyverse workflow:

```{r exampleTwo, comment=NA}
# Correlation report
cor.test(iris$Sepal.Length, iris$Petal.Length) %>% 
  report()
```

## Example 3

You can also create tables with the `table_short()` and `table_long()`
functions. For example, create a table report for a linear model.
We can use the `kable()` function from `KableExtra` to get a nicely
formatted table.

```{r exampleThree, comment=NA}
kable(
lm(Sepal.Length ~ Petal.Length + Species, data=iris) %>% 
  report() %>% 
  table_short()
)
```

# Supported Packages

Currently supported objects by report include `cor.test`, `t.test`,
`correlation`, `glm`, `lme4::merMod`, `rstanarm::stanreg`, `modelbased`.

## t-tests and correlations

```{r exampleFour, comment=NA, warning=FALSE}
t.test(mtcars$mpg ~ mtcars$am) %>% 
  report()
```


# Miscellaneous

## Report participants details

```{r exampleFiveA, comment=NA, warning=FALSE}
data <- data.frame("Age" = c(22, 23, 54, 21),
                   "Sex" = c("F", "F", "M", "M"))
```

```
Not even the dev version worked
{r exampleFiveB}
paste(report_participants(data, spell_n = TRUE),
      "were recruited in the study by means of torture and coercion.")
```
The example above fails with
```
Error in UseMethod("format_value") : no applicable method for 'format_value' applied to an object of class "NULL"
```


# Credits

If you like it, you can put a star on this repo, and cite the package
as follows:

Makowski & Lüdecke (2019). The report package for R: Ensuring the use of best practices for results reporting. CRAN.


