---
title: "test-opti-png"
author: "John Minter"
date: "Started: 2018-02-16, Last modified: 2019-02-23"
output:
  html_document:
    keep_md: true
    variant: github_md
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
knit_hooks$set(optipng = hook_optipng)
knit_hooks$set(pngquant = hook_pngquant)
```

# Load a spectrum

First we get our exemplar **.msa** format spectrum file. I had included
the file in the `rEDS` package. We will suppress the messages where R
has loaded the required packages by using the optional `quietly` 
variable.

```{r}
library(rEDS, quietly=TRUE)
fi <- system.file("extdata", "Benitoite.msa", package = "rEDS")
print(fi)
```

Next, we create a Spectrum object using the `SingleMSA` function.
You can get the help page by typing `??rEDS::singleMSA` into the
R console.

```{r, message=FALSE}
spc <- singleMSA(fi, probecur=2.5)
```

and now we can plot the spectrum.

```{r, fig.width=7}
plot(spc, maxEnergy=10000, doLog=TRUE, optipng = '-o7')
```

We can also create a ggplot with a linear intensity scale. You can
get the help page by typing `??rEDS::ggplotSpectrumLinY` into the 
R console.

```{r, fig.width=7, optipng = '-o7'}
plt <- ggplotSpectrumLinY(fi, "Benitoite", 0.2, 7.0, 1.0, 2.5)
print(plt)
```

next we will make a plot with a logarithmic intensity

```{r, fig.width=7, optipng = '-o7'}
plt <-ggplotSpectrumLogY(fi, "Benitoite", 0.2, 7.0, 1.0, 2.5)
print(plt)
```

# To preview in Sublime Text 3

0. Install [MarkdownLivePreview](https://github.com/math2001/MarkdownLivePreview)
   I had to do this using git:

```
$ cd "%APPDATA%\Sublime Text 3\Packages"             # on Windows
$ cd ~/Library/Application\ Support/Sublime\ Text\ 3 # on Mac
$ cd ~/.config/sublime-text-3                        # on Linux

$ git clone "https://github.com/math2001/MarkdownLivePreview"
```

1. `Ctl+Shift+P` to get the `Command Pallette`
2. Go down to `Markdown Preview: Preview in Browser` and click
3. Choose either `markdown` or `github`.

# Sources of info

1. [www.zevross.com](https://www.zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/): Tips and tricks for working with images and figures in R Markdown documents.

2. [rforge.net](https://www.rforge.net/doc/packages/knitr/chunk_hook.html): Built-in chunk hooks to extend knitr.

3. [optipng.sourceforge.net](http://optipng.sourceforge.net/): The OptiPng home page.

4. [Yihui Xie, Dynamic Documents with R and knitr, Second Edition, Section 10.24](https://books.google.com/books?id=fyIuDwAAQBAJ&pg=PT130&lpg=PT130&dq=R+optipng+example&source=bl&ots=QGT_81jnc_&sig=g8l-VrVUDFzlxjU30BL7S7fXt5w&hl=en&sa=X&ved=0ahUKEwjR9di78avZAhVG7YMKHTsPCcoQ6AEIgwEwCA#v=onepage&q=Optimize%20PNG%20Plots&f=false): Yihui's example with OpiPng.

