---
title: "rFlair"
author: "Kelly Bodwin"
date: "2020-05-04"
output:
  html_document:
    css: ./theme/jm-gray-vignette.css
    number_sections: yes
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```


<style type="text/css">
.main-container {
  max-width: 750px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r loadPackages, message=FALSE}
library(readr)
library(flair)
library(here)
library(dplyr)
library(ggplot2)
```

It is my distinct pleasure today to introduce you to the `flair` package.

The following is an example of the type of classroom disaster that motivated
this package:

You are presenting an analysis to a class or audience, and you turn to a slide
where you show both source code and its output. Because you wanted to emphasize
a line of the source code, you copy-pasted the code text into the slide, and
added highlighting to the relevant section.

Upon opening the slide, you realize with creeping horror that you made a change
in the source code, but you forgot to edit your slide. The code text displayed
on your screen no longer matches the output, and your students are confused.

Was this relatable? Have you, too, lived out this horror story?

This kind of un-reproducibility of materials, and the simple frustration of the
fiddly nature of manually highlighting code text, led me to develop flair.
I wrote this package first and foremost for educators, although I have found 
it equally useful for conference talks and workshops.

You can find the basic package documentation and vignettes at this site. Today,
though, I want to take the time to show you a few of my favorite examples of
flair in action, to give you an idea of how it might be useful in your classroom
or presentation.

These examples all use the baby_names dataset from 
[here](https://www.kaggle.com/kaggle/us-baby-names), which contains counts of
babies born with each given name, in each state, since the 1800s. We’ll restrict
our data only to babies born in California with the first name “Kelly”. You can
download this data to follow along.

Example 1: Emphasize small differences in code.

The most default ability of flair is quickly adding basic highlighting to code.

There are a lot of use cases of this simple functionality. I am particularly
fond of using the `flair()` function to show how small changes in code impact
the output.

For example, suppose I am teaching the concept of geometries in ggplot. I wish
to plot the number of babies born each year with the name “Kelly” in California,
colored by gender assigned at birth.

I have made two different plots; one using columns, and one using lines. The
code chunk for my work looks like this:


```{r loadDataset}

# pa <- paste0(here::here(), "/nyc_baby_names.csv")
pa <- paste0(here::here(), "/kelly_ca.csv")
pa

baby_names <- read_csv(pa)
# names(df)[1]<-paste("Year")
names(baby_names)
```

Plot the distribution

```{r geoms, include=FALSE}
baby_names %>%
  ggplot(aes(x = Year, y = Count, fill = Gender)) +
  geom_col()

baby_names %>%
  ggplot(aes(x = Year, y = Count, color = Gender)) +
  geom_line()
```


With the decorate and flair functions, I can trigger this code chunk to be
evaluated, while simultaneously adding highlighting to the chosen parts of my
code.

Ordinarily, we would use echo = FALSE on the first chunk below, so as not to
see the `flair()` process.

```{r foo}
decorate("geoms") %>%
  flair("_col") %>%
  flair("fill = ") %>%
  flair("_line") %>%
  flair("color = ")
```


And the plot

```{r plotWithFlair1}
baby_names %>%
  ggplot(aes(x = Year, y = Count, fill = Gender)) +
  geom_col()

```



