---
title: "Font Test"
author: "dlsweet"
date: "October 18, 2017"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{fontspec}
  - \setmainfont{FreeSans}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

There was a post by user `dlsweet`  on
[RStudio Community](https://community.rstudio.com/t/custom-fonts-in-rmarkdown-pdf/2098/2)
concerning the YAML for a PDF document to specify fonts. The solutio was to
include informtion in the `header-includes:` section of the YAML. The original
used the font `Museo` which I do not have. To test, I tried `FreeSans`

It is not clear how to download Adobe Fonts

`dlsweet` reaponded to Mara Averick...

> Thanks @mara, I didn't have to quite override them separately but you gave me
> the idea to try moving my LaTex command into my YAML Header.



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
