---
title: "Where does all the Bourbon come from?"
author: "J. D. Long"
date: "2020-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

From [twitter](https://twitter.com/CMastication/status/1256259572664336384)

Posted 2020-05-01.

```{r loadPackages, message=FALSE}
library(tmap)
library(spData)
library(tidyverse)
```

We will get the `spData` package to provide the `us_states` dataset.
This is a Formal class 'sf. The data contains a data.frame with
49 obs. of 7 variables:

- `GEOID` character vector of geographic identifiers

- `NAME` character vector of state names

- `REGION` character vector of region names

- `AREA` area in square kilometers of units class

- `total_pop_10` numerical vector of `total population` in 2010

- `total_pop_15` numerical vector of total population in 2015

- `geometry` sfc_MULTIPOLYGON

The object is in geographical coordinates using the `NAD83` datum.

Note that we can get more date by installing a larger dataset.

```
install.packages('spDataLarge',
                 repos='https://nowosad.github.io/drat/',
                 type='source')
```

Let's show where Kentucky bourbon is produced.

```{r loadModel}
us_states %>%
  mutate(Bourbon =
           case_when(NAME =="Kentucky" ~ ">1",
                     TRUE ~ "<1")) ->
  us_states_bourbon

tm_shape(us_states_bourbon) +
  tm_fill(col = "Bourbon",
          title = "Barrells per Capita") +
  tm_style("col_blind") +
  tm_layout(main.title = "Kentucky Bourbon Barrels per Capita by State",
            main.title.position = "center" )

```


