---
title: "TestAcademicWriter"
author: "John Minter"
date: "4/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

```{r loadPackages, message=FALSE}
library(academicWriteR)
library(kableExtra)

```

```{r testOne}

round_pval(0.03765) 
round_pval(0.0000001)
round_pval(0.07)

```

# Printing functions

The printing functions were made to facilitate reporting statistical models
in RMarkdown using `papaja`. `papaja` comes with it’s own printing
functions but I found that I am constantly tinkering with them to get
things to work the way I prefer, thus I decided to make my own.

The first is a wrapper around the round_pval function: `print_pval`.

P-values are printed exactly unless they are less than 0.001.
Trailing 0’s are deleted. We first set `latex` to `FALSE`

```{r testPrintOne}
print_pval(0.03765, latex = FALSE)
```

Next, we first set `latex` to `FALSE`

```{r testPrintTwo}
print_pval(0.0765, latex = TRUE)
```

# lm() example

The printing functions are used for reporting the results of statistical
analyses. There are designed to be used in in-line knitr chunks
(i.e., `r 1 + 1`) in an RMarkdown document. Instead of going in to more
detail here, I will just work through and example. First, I will fit a
linear model with the lm function.

```{r fitLinearModel}
lm_mod1 <- lm(mpg ~ wt, data = mtcars)
summary(lm_mod1)$coef
```

In a typical write-up of the results we might say something like:

```
Miles per gallon varied as a function of weight (wt). Specifically, a
1-unit increase in weight was associated with a decrease in mpg of -5.34
+/- 0.56 standard errors (CI = [-6.49, -4.2]; t = -9.56; p < .001).
```

The aforementioned sentence was written in RMarkdown like this:

Miles per gallon varied as a function of `weight` (wt). Specifically, a
1-unit increase in weight was associated with a decrease in `mpg` of 
`r print_model_params(model = lm_mod1, predictor = 'wt', parameter = 'estimate')` 
+/- `r print_model_params(model = lm_mod1, predictor = 'wt', parameter = 'std.error')`
standard errors `r print_model_params_p(model = lm_mod1, predictor = "wt", latex = FALSE)`

Here I use two print functions: print_model_params and print_model_params_p. The _p variant referes to parenthesis. In other words it prints the parameter information that I typically put between parenthesis. Notice each in-line chunk is given it’s own line (more on this below).

# lmer() example

Here is another example using lme4 objects. Sadly, `kable` doesn't get
formatting right...

```{r lmerExample}
library(lme4)
library(lmerTest)
library(broom.mixed)
lmer_mod0 <- lmer(Reaction ~ 1 + (1|Subject), data = sleepstudy, REML = F)
lmer_mod1 <- lmer(Reaction ~ 1 + Days + (1|Subject), data = sleepstudy, REML = F)
model_comparison <- anova(lmer_mod0, lmer_mod1, test = 'Chisq')
summary(lmer_mod1)$coef
```

And a possible write-up:

> There was a main effect of days (χ2(1) = 116.46; p < .001).
> Specifically, a change of one day was associated with an increase in
> reaction time of 10.47 ms +/- 0.8 standard errors (CI = [8.9, 12.04];
> t = 13.06; p < .001).

The above paragraph was written as follows:

**There was a main effect of days (χ<sup>2</sup>(1) = 116.46; *p* \< 0.001). Specifically, a change of one day was associated with an increase
in reaction time of 10.47 ms +/- 0.8 standard errors (CI = \[8.9,
12.04\]; *t* = 13.06; *p* \< .001).**

If you don’t interpret the effect directly in the prose you can print
all the parameters at once using `print_model_param(model, parameter)`.

```{r doThePrint, echo=FALSE}
print_model_param(lm_mod1, "(Intercept)", latex = F)
```

```
print_model_param(lmer_mod1, "(Intercept)", latex = F)
```

