---
title: "Test ggridges"
author: "John Minter"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

First, load the libraries and set a path to save the plot. In this case,
the weather data, `lincoln_weather`, comes from the `ggridges` package.
The `here` package makes it easy to deal with file paths. The `ggplot2`
packages lets us build up a plot.

```{r loadLibaries, message=FALSE}
library(ggplot2)
library(ggridges)
library(here)

pa <- here::here()
fi <- paste0(pa, "/plt/lincoln_nebraska_weather.png")
```

Here we use ggplot to plot the mean temperature [F] as the x-axis,
the month as the Y axis, and filling using the `stat()` called with
the x value (mean temperature). The plot will automatically render
in the output report.

```{r makePlot, fig.align = 'center'}
plt <- ggplot(lincoln_weather,
              aes(x = `Mean Temperature [F]`,
                  y = Month, fill = stat(x))) +
       geom_density_ridges_gradient(scale = 3,
                                    rel_min_height = 0.01,
                                    gradient_lwd = 1.) +
       scale_x_continuous(expand = c(0, 0)) +
       scale_y_discrete(expand = expansion(mult = c(0.01, 0.25))) +
       scale_fill_viridis_c(name = "Temp. [F]", option = "C") +
       labs(title = 'Temperatures in Lincoln NE',
            subtitle = 'Mean temperatures (Fahrenheit) by month for 2016') +
      theme_ridges(font_size = 13, grid = TRUE) + 
      theme(axis.title.y = element_blank())

plt
```

We also want to save the plot as a `.png` file. We use the function `ggsave()`.
We could (manually) add this image to a PowerPoint presentation. We could also
modify this code to generate the PowerPoint slide deck...

```{r savePng}
ggsave(plt, file=fi, width=9.0, height=6.0, units="in", dpi=300)
```
