---
title: "Analyze Titration"
author: "John Minter"
date: "2020-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, comment=NA)
```

Take as an example the Royal Australian Chemical Institute's (RACI)
schools titration competition of 1997. In this competition, each of a
team of three high school students is asked to measure the concentration
of a solution of acetic acid, given a solution of sodium hydroxide and
a solution of hydrochloric acid of known concentration.

The members of the team use the hydrochloric acid solution to standardize
the sodium hydroxide solution, which in turn is used to titrate the acetic
acid solution. In table 1.2 are the results of one member of each of
25 teams that participated in the competition in 1997 at the University
of New South Wales, Sydney Australia. Although no one is spot on, there
are some very near misses and some pretty woeful answers (e.g., 0.9083M).
We know that the students were not given enough sodium hydroxide to
titrate 25 mL of 0.9083 M acetic acid, so we can confidently say that
this is a gross error in calculation or recording the result.

Plotting the results in increasing order of magnitude reveals some
interesting groupings (figure 1.2). The high result is clearly off
the planet, as can be seen from figure 1.2, but we will show that six
other results can also be classed as outliers by methods we explain in
chapter 3. The remaining data are shown to group around the accepted
answer, and within limits of an expected random scatter, calculated
from an analysis like the one above for the pipette, but covering all
sources of uncertainty. Out of the 25 results, seven are rejected
as gross errors and of the remainder seven fall above and 11 fall
below the correct answer. Plotting a histogram, a bar chart of
how many results fall within given ranges, reveals the distinction
between the random error and the outliers. (JRM note: I used R and
ggplot2 to do this analysis from the tabulated data)


D. Brynn Hibbert;J. Justin Gooding. Data Analysis for Chemistry:
An Introductory Guide for Students and Laboratory Scientists (p. 28).
Kindle Edition. 

# Load Packages

```{r loadPackages, message=FALSE}
library(readr)
library(here)
library(ggplot2)
library(kableExtra)

pa <- paste0(here::here(), "/dat/1997_RACI_Titration.csv")
df <- as.data.frame(read_csv(pa))
```
Note an obvious outlier by student 14.

```{r printData}
print(df, row.names = FALSE)
```

Remove the outlier by setting the value to `NA`

```{r removeOutlier}
df$M[14] <- NA
```

Plot the distribution

```{r removeBigOutlier, warning=FALSE}

xMin = 0.09
xMax = 0.12
deltaX = 0.01

yMin = 0.0
yMax = 6.0
deltaY = 0.5

plt2 <- ggplot(df, aes(x=df$M)) +
        geom_histogram(binwidth=0.0005,
                       color="gray",
                       fill="darkblue") +
        xlab("concentration [M]") +
        ylab("counts") +
        scale_x_continuous(breaks = seq(from=xMin, to=xMax, by=deltaX),
                           limits = c(xMin, xMax)) +
        scale_y_continuous(breaks = seq(from=yMin, to=yMax, by=deltaY),
                           limits = c(yMin, yMax)) +
        ggtitle("1997 RACI Titration Competition (1 gross outlier removed)") +
        theme(axis.text=element_text(size=12),
              axis.title=element_text(size=12),
              plot.title=element_text(hjust = 0.5)) + # center the title
        NULL
print(plt2)

```


